---
title: "BIS15L_AI_class"
author: "Jocelyn Morales"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
Today, we're exploring how AI can aid in writing, comprehending and troubleshooting our R code. AI is a very valuable tool, but it's important not to rely on it entirely. Building a strong R foundation is still important. These AI tools are not perfect and can be inaccurate solutions. In addition these tools can't read our minds, so understanding R helps us generate better prompts to get better responses. In short, AI should be used as a tool, not a crutch. Additionally, do not forget about other useful resources like Stack Overflow/Exchange, online tutorials, and GitHub issues pages for learning and troubleshooting. Let's combine AI with traditional methods to master R effectively.

This overview isn't exhaustive of all possible AI tools for R coding, but I believe it is a good start and covers everything you need.


**Make sure to enable Github Copilot in RStudio.**
Go to Tools -> Global Options -> Copilot -> Enable Git

## Learning Goals: 
*At the end of this exercise, you will be able to:*  
1. Explain what AI is and what AI tools can be used for R.
2. Enable Github Copilot in RStudio.
3. Use Copilot/ChatGPT to write code in RStudio.
4. Use Copilot/ChatGPT for troubleshooting code in RStudio.


## Exploration Questions:
Lets get some get a feel for what copilot (or ChatGPT) does, use Github Copilot to autocomplete the questions below. You can alternatively paste the questions in ChatGPT or Microsoft Copilot.
1. What is AI?
So, Artificial Intelligence (AI) is like giving computers a brain to do smart stuff, kinda like what humans do. There are two main types: one that's good at specific tasks, and another that's like super-smart but we're still figuring that out.

AI learns from data, like a computer getting better at something over time (we call it Machine Learning). There's also a fancy version called Deep Learning, which is like giving the computer a really complex brain.

People use AI in lots of cool areas, like making healthcare smarter, helping with money stuff, and even making cars drive themselves. It's all about making computers awesome at doing smart things!

2. What is ChatGPT?
ChatGPT is like a computer that's really good at talking. It understands what you say and responds in a way that makes sense. You can have a conversation with it by typing or asking questions, and it tries its best to chat with you like a human. It's made by OpenAI and is part of their work on making computers understand and generate human-like text. Keep in mind, though, it has some limits and might not always get things exactly right!

3. What is Github Copilot?
GitHub Copilot is like a coding buddy that helps developers write code faster. It suggests code as you type, completing whole lines or blocks based on what you're working on. It's pretty smart, understanding the context of your code, and it can handle various programming languages. The cool part is it learned a lot from tons of publicly available code, so it's like having a coding companion that's seen a bunch of examples and knows how to help you out. Just keep in mind, it's handy but might not be perfect for every situation!

4. What is the simplests form to use 

## Load the libraries  
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(dplyr)
library(shiny)
library(shinydashboard)
```

## Load the Data: 
```{r}
#load the Netflix Data in your Data folder, save it under the object name Netflix
netflix <- read_csv("data/netflix_titles.csv")
```

*Did copilot help you write the code above? Could anything about the prompt be improved to help Copilot understand what you want to do more accurately?*


## Lets Practice:
Explore the elements in your data: include a comment within your code chunk to prompt Copilot to use the function of your choice
```{r}
glimpse(netflix)

```
*Did copilot use your preferred method to get the summary of the data? If not, how could you improve the prompt to get the desired output?*


Sort out the movies from the netflix into an new object called netflix_movies
```{r} 
netflix_movies <- filter(netflix, type=="Movie")
```


Which director has the most movies on netflix?
```{r}


```
*Do you see anything wrong with the table above, look at row 1. Write a prompt below to fix this.*

filter directors with the most movies but remove NAs (chatgpt)
```{r}
filter(count(netflix_movies, director, sort = T), !is.na(director))
```



Which director had the most movies by release year and remove the NA's? (chatgpt)
```{r}
netflix_movies %>%
  group_by(director) %>%
  summarise(missing_count = sum(is.na(director)), .groups = 'drop') %>%
  arrange(desc(missing_count))

netflix_movies %>%
  filter(!is.na(director))
```
*See anything else interesting about this table, look at the first director on the table. Could this be a problem and how can we edit the dataset to fix this? Try writing a prompt.*


how to separate two directors shown together (chatgpt)
```{r}
netflix_movies %>%
  filter(!is.na(director)) %>%
  separate_rows(director, sep = ",\\s*") %>%
  group_by(director) %>%
  summarise(movie_count = n(), .groups = 'drop') %>%
  arrange(desc(movie_count))
```

Make a bar plot of the top directors with the most movies on netflix
```{r}
netflix_movies %>%
  filter(director != "NA") %>%
  group_by(director) %>%
  summarise(title = n(), .groups = 'drop') %>%
  arrange(desc(title)) %>% 
  ggplot(aes(x = reorder(director, -title), y = title)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Top Directors with the Most Movies on Netflix",
       x = "Director",
       y = "Number of Movies") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
*Do you see any issues with this plot? How could we improve the prompt to get a better boxplot? Try writing a prompt.*

[Insert your prompt here]
```{r}

```

*How about for just 2020*



[Insert your prompt here]
```{r}

```


*Take a few minutes to make your own plot(s) using prompts, edit prompts until you get a plot that you like.*






## Lets make the top 10 directors barplot into a Shiny App: use copilot or Chatgpt


*Now use ChatGPT, Copilot or previous notes to fix the code*
```{r}
data_for_plot <- netflix_movies %>%
  filter(!is.na(director)) %>%
  group_by(director) %>%
  summarise(title = n(), .groups = 'drop') %>%
  arrange(desc(title))

ui <- fluidPage(
  titlePanel("Netflix Movies by Director"),
  sidebarLayout(
    sidebarPanel(),
    mainPanel(
      plotOutput("barplot")
    )
  )
)

server <- function(input, output) {
  output$barplot <- renderPlot({
    ggplot(data_for_plot, aes(x = reorder(director, -title), y = title)) +
      geom_bar(stat = "identity", fill = "blue") +
      labs(title = "Top Directors with the Most Movies on Netflix",
           x = "Director",
           y = "Number of Movies") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
  })
}

shinyApp(ui, server)
```


## That's it! Let's take a break and then move on to working on group projects.
